---
title: "PML Project"
output: html_document
Auther: ahalawa
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary
This report gavies a brief explanation to how to use the https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv dataset to make the predictions. Fristly I explore the data, clean the data, train the model, and then make predicttion.

```{r }
#Loding libraries

library(ggplot2)
library(caret)
library(randomForest)
```

## read training and test datasets

```{r}
trainData <- read.csv("D:/Abdelrahman/data science/wd/pml-training.csv", na.strings=c("NA", ""))
testData <- read.csv("D:/Abdelrahman/data science/wd/pml-testing.csv",na.strings=c("NA", ""))
```

## Exploratory Analysis
```{r}
dim(trainData)
head(trainData)
```

## Data Cleaning and Feature Engineering
```{r}
#remove unrelated columns
trainData<-trainData[,-which(names(trainData)=="cvtd_timestamp")]
trainData<-trainData[,-which(names(trainData)=="user_name")]

#calculate NA ratio per column
naPerCol <- as.data.frame(colSums(is.na(trainData))/nrow(trainData))
names(naPerCol)<-"na"
#only select the columns that have no missing values.
naPerCol<-subset(naPerCol, na ==0)
trainData<-trainData[,rownames(naPerCol)]

```

## Model Training (including cross-validation)
I will use Random Forest model, because it always gives high accuracy as a role of thumb.  

```{r}
# split the data
set.seed(5412)
inTrain <- createDataPartition(y=trainData$classe, p = 0.7, list=FALSE)
trainingSet <- trainData[inTrain,]
testingSet <- trainData[-inTrain,]
#model
model <-  randomForest(classe ~. , data=trainingSet, method="class")

#Cross Validation:- To sense of the out of sample error.
pred<-predict(model,testingSet)
cm<-confusionMatrix(pred,testingSet$classe)
cm$overall['Accuracy']
cm$table
```
As I expected RF gives high accuracy.

##conclusion
Random Forest algorithm performed better with Accuracy 100%.Thus, the sample error rate 0%

## Quiz

```{r, echo= TRUE ,results=FALSE}
qCol<-subset(rownames(naPerCol),rownames(naPerCol)!="classe")
testData<-testData[,qCol]
predict(model,testData)

```

















